\documentclass[12pt]{article}
\pdfoutput=1

\usepackage{graphics,amssymb,float}
%\usepackage[usenames,dvips]{color}
\usepackage{graphicx}% Include figure files
\usepackage{subfigure}
\usepackage{color}
\usepackage{xspace}
\usepackage{placeins}
%\usepackage[color]{showkeys}
%\usepackage{epsfig}% Include figure files
\usepackage{rotating}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{cite}
\usepackage{amsmath}
\usepackage{indentfirst} % activate indent in the first paragraph
\usepackage{epstopdf}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}

\bibliographystyle{utphys}


\textheight=22.8 truecm
\textwidth=17 truecm
\topmargin=-3mm
\voffset=-1 truecm
\hoffset=-2 truecm

\def\eg{{\it e.g.}}
\def\ie{{\it i.e.}}
\def\mgut{M_{\rm GUT}}

\def\Eq#1{Eq.~(\ref{#1})}
%\def\Eqs#2{Eqs.~(\ref{#1})--\ref{#2})}

\def\lsim{\mathrel{\raise.3ex\hbox{$<$\kern-.75em\lower1ex\hbox{$\sim$}}}}
\def\gsim{\mathrel{\raise.3ex\hbox{$>$\kern-.75em\lower1ex\hbox{$\sim$}}}}
\def\ifmath#1{\relax\ifmmode #1\else $#1$\fi}

\def\change{\marginpar{\bf text changed}}
\def\new{\marginpar{\bf new addition}}
\def\check{\marginpar{\bf check!}}

\begin{document}
%\begin{titlepage}
\begin{center}


%\vspace*{-1cm}
\begin{flushright}
preprint numbers
%LAPTH-061/12\\
%LPSC12350\\
%LPT Orsay 12-119\\
%NSF-KITP-12-236
\end{flushright}

\vspace*{1.6cm}
{\Large\bf A survey of supersymmetry\\[3mm] based on simplified-model results from the LHC} 

\vspace*{1cm}\renewcommand{\thefootnote}{\fnsymbol{footnote}}

{\large 
%B.~Dumont$^{1}$\footnote[2]{Email: dumont@lpsc.in2p3.fr},
Sabine~Kraml$^{1}$\footnote[1]{Email: sabine.kraml@lpsc.in2p3.fr},
Suchita~Kulkarni$^{1}$\footnote[2]{Email: suchita.kulkarni@lpsc.in2p3.fr},
Wolfgang Waltenberger$^{2}$\footnote[3]{Email: wolfgang.waltenberger@oeaw.ac.at}
} 

\renewcommand{\thefootnote}{\arabic{footnote}}

\vspace*{1cm} 
{\normalsize \it 
$^1\,$Laboratoire de Physique Subatomique et de Cosmologie, UJF Grenoble 1,
CNRS/IN2P3, INPG, 53 Avenue des Martyrs, F-38026 Grenoble, France\\[2mm]
$^2\,$Institut f\"ur Hochenergiephysik,  \"Osterreichische Akademie der Wissenschaften,\\ Nikolsdorfer Gasse 18, 1050 Wien, Austria\\[1mm]
}

\vspace{1cm}

\begin{abstract}
  Abstract
\end{abstract}

\end{center}

%\end{titlepage}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Searches at the ATLAS and CMS experiments at the LHC show no signs of new physics whatsoever. 
After the first phase of LHC operation at centre-of-mass energies of 7--8~TeV in 2010--2012, 
the limits for the masses of supersymmetric particles, in particular of  squarks and gluinos, 
have been pushed well into the TeV range~\cite{atlas:susy:twiki,cms:susy:twiki}. 
%See \cite{atlas:susy:twiki,cms:susy:twiki} for the latest results.
Likewise, precision measurements in the flavor sector, in particular in $B$-physics, 
are well consistent with Standard Model (SM) expectations~\cite{Amhis:2012bh,lhcb:2012ct} 
and show no sign, or need, of new physics. 
At the same time the recent discovery~\cite{atlas:2012gk,cms:2012gu} of a Higgs-like particle 
with mass around 125~GeV makes the question of stability of the electroweak scale---the 
infamous gauge hierarchy problem---even  more imminent. 
Indeed, supersymmetry (SUSY) is arguably the best-motivated theory to solve the gauge 
hierarchy problem and to explain a light SM-like Higgs boson. 
So, the Higgs has very likely been discovered---but where is supersymmetry? 

Looking closely \cite{Sekmen:2011cz,Arbey:2011un,Papucci:2011wy,CahillRowley:2012kx,Dreiner:2012gx,Mahbubani:2012qq} 
one soon realizes that many of the current limits on SUSY particles are based 
on severe model assumptions, which impose particular relations between particle masses, decay 
branching rations, {\it etc}. The prime example is the interpretation of the search results within the 
Constrained Minimal Supersymmetric Standard Model (CMSSM). Another approach, which   
has become quite standard for the experiments, is to interpret the results 
within so-called Simplified Model Spectra \cite{Okawa:2011xg,cms:2013wc}.  
Simplified Model Spectra, or SMS for short, are effective-Lagrangian descriptions involving %the interactions of 
just a small number of new particles. They were designed as a useful tool for the characterization 
of new physics, see \eg\ \cite{Alwall:2008ag,Alves:2011wf}. 
On the whole, a large variety of results on searches in many different channels\footnote{Unfortunately with large variations in the level of documentation and details given on the analyses.} are available from both ATLAS and CMS, but it is quite difficult to determine whether a particular parameter point or scenario is allowed or excluded. 

In this paper, we present a method to decompose the signal of an arbitrary SUSY spectrum into simplified model  
topologies and thus test it against all the existing bounds derived in the SMS context. 
As we will show, this allows a vast survey of general and less general SUSY models, and enormously simplifies the task of designing the regions of parameter space which are still allowed, and/or have not yet been explored, by the current searches.
A scan over a 7-parameter realization of the MSSM is used as a show-case example to demonstrate the power of our method. 
Even in this example of limited complexity (as compared to, \eg, the 19-parameter phenomenological MSSM or the completely general MSSM with more than 100 free parameters) it turns out that large regions of interesting parameter space with SUSY particles below 1~TeV %survive the current bounds. 
remain unchallenged by the current bounds.

%The question what we really know about SUSY in general has been adressed in \cite{Sekmen:2011cz,Arbey:2011un,Papucci:2011wy,CahillRowley:2012kx} and some loopholes for evading the mainstream limits have been pointed out in, \eg, \cite{Dreiner:2012gx,Mahbubani:2012qq}. A recast of SMS limits onto minimal supergravity was attempted in \cite{Gutschow:2012pw}.

\input{SMSintro}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Decomposition into simplified model topologies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{SMSdecomposition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Parameter scan}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

For the sake of definiteness we scan over a 7 parameter semi-constrained version of the MSSM 
with parameters defined at the GUT scale. 
Concretely, we take a universal gaugino mass parameter $M_{1/2}$,  as well as common scalar mass parameters 
for first and second generation sfermions ($M_{0,1}$) and third generation sfermions ($M_{0,3}$) at $\mgut$.  
We also assume a common trilinear coupling $A_0\equiv A_t=A_b=A_\tau$ at $\mgut$. 
Regarding the Higgs sector,  we trade $M_{H_u}^2$ and $M_{H_d}^2$ at $\mgut$ against 
$\mu$ and $m_A$ at the SUSY scale. Finally, we need the ratio of the two Higgs VEVs, $\tan\beta=v_2/v_1$, 
which we define at the weak scale. 
The scan ranges are given in Table~\ref{tab:scan}.

\begin{table}[t]\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|}
  \hline
  $M_{1/2}$ & $M_{0,1}$ & $M_{0,3}$ & $A_0$ & $m_A$ & $\mu$ & $\tan\beta$ \\ 
  \hline
  0.1\,--\,1 & 0\,--\,3 & 0\,--\,1 & $-3$\,--\,3 & 0.1\,--\,2 & 0.1\,--\,1 & 2\,--\,50 \\
  \hline
\end{tabular}
\caption{Scan ranges used in this study. Dimensionful quantities are in TeV units.}
\label{tab:scan}
\end{table}

\marginpar{\bf add versions and refs}
We use SOFTSUSY for the computation of the masses and mixings,  SUPERISO for flavor observables, 
micrOMEGAs for dark matter observables and particle decay tables, and HDECAY for computing Higgs decays.
For the SM input values, we use $m_t=....$, $m_b(m_b)=4.19$~GeV, and $\alpha_s(M_Z)=0.1187$ ????  
We require a neutralino LSP.  
The constraints imposed are listed in Table~\ref{tab:constraints}.

\begin{table}[t]\centering
\begin{tabular}{|c|c|c|c|c|}
\hline
  \bf Observable  & \bf Experimental result   & \bf TH uncertainty & \bf Constraint imposed \\
\hline
 BR$(b \rightarrow s\gamma) $ & $(3.55 \pm 0.23 \pm 0.09)\times 10^{-4}$ \cite{Amhis:2012bh} & $0.24 \times 10^{-4}$ & $[2.86,\,4.24] \times 10^{-4}$  \\
\hline
BR$(B_s \rightarrow \mu^+ \mu^-)$ & $3.2^{+1.5}_{-1.2} \times 10^{-9}$ \cite{lhcb:2012ct} & 10\% & $[0.7,\,6.3] \times 10^{-9}$\\
\hline
$\Delta a_\mu$ & $(26.1 \pm 8.0)\times 10^{-10}$ \cite{Hagiwara:2011af} & $10\times 10^{-10}$ & $[-0.5,\,51.7] \times 10^{-10}$ \\
\hline
$\Omega h^2$ & $0.1123\pm 0.0055$~\cite{} & 10\% & $<0.136$ \\
\hline
$m_h$ & $125.2\pm 0.3\pm 0.6$ GeV (ATLAS) & 3~GeV \cite{xxx} & $125.5\pm 3$~GeV \\
              & $125.8\pm 0.4\pm 0.4$ GeV (CMS)\phantom{00} & &  \\
\hline
 sparticle masses & LEP  & --- & (micrOMEGAs) \\
\hline
\end{tabular}
\caption{Constraints used to define the valid parameter space before applying the SMS limits.}
\label{tab:constraints}
\end{table}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgements} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This work was supported in part by the by the French 
ANR project {\sc DMAstroLHC}. %BLAN12-???.

\begin{appendix}
\input{SMSappendix}
\end{appendix}


\bibliography{references}

\end{document}

